Template report example

### 2024-03-11 dev/dev_template_report.Rmd

---
title: Template report example
subtitle: subtitle
author:
  name: author
  email: email@example.com
  affiliation: "name <br> address"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    theme: paper
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

# Libraries
library(knitr)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(plotly)
library(StreamFind)

# Variables
logo <- NA_character_

# Global options
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.width = 9, results = "asis")

# Working directory
path_wd <- getwd()

# Add logo file
path_extdata <- system.file(package = "StreamFindData", dir = "extdata")
logo <- file.path(path_extdata, "logo_iuta.png") #207 x 216 px
```

```{r logo, echo=FALSE}
if (!is.na(logo)) {
  htmltools::img(
  src = knitr::image_uri(logo),
  alt = "logo",
  style =
    paste0("
      margin-left:inherit;
      position:absolute;
      top:60px;
      left:740px;
      width:", 100, "px;
      height:", 100*(216/207), "px;"
    )
  ) 
}
```

@@

Code is automaticelly embedded unless `echo` chunk option is set to `FALSE`.
Evaluation of code in a given chunk can be skiped by setting `eval` to `FALSE`.
Code chunks should always be unically named.

@@

<br> <br>

@@

The report was produced on `r Sys.time()`. The data and report are stored in ``r path_wd`` of the workstation *`r Sys.info()["nodename"]`* under the user *`r Sys.info()["user"]`*.

@@

<style>
body, p {
  color: black;
  font-family: Arial;
  text-align: justify;
  font-size: 12pt;
}
h1{
  font-size: 20pt;
  font-style: bold;
}
h2{
  font-size:18pt;
  font-style: bold;
}
h3{
  font-size:14pt;
  font-style: bold;
}
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #239B56;
}
caption {
  color: black;
  font-size: 1.0em;
}
</style>

>>>>

---
title: Template report example
subtitle: subtitle
author:
  name: author
  email: email@example.com
  affiliation: "name <br> address"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    theme: paper
editor_options: 
  chunk_output_type: console
---
<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
  background-color: #1E8449;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.width = 9, results = "asis", cache = TRUE, comment = '')
options(width = 400)
```

```{r libraries, include=FALSE}
library(knitr)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(plotly)
library(StreamFind)
```

```{r logo, echo=FALSE}
path_extdata <- system.file(package = "StreamFindData", dir = "extdata")
logo <- file.path(path_extdata, "logo_StreamFind.png")
htmltools::img(src = knitr::image_uri(logo), style = "margin-left:inherit;position:absolute;top:100px;left:740px;width:200px;")
```

@@

Code is automatically embedded unless `echo` chunk option is set to `FALSE`.
Evaluation of code in a given chunk can be skiped by setting `eval` to `FALSE`.
Each code chunk should have a unique named.

@@

@@

The report was produced on `r Sys.time()`. The data and report are stored in `r getwd()` of the workstation *`r Sys.info()["nodename"]`* under the user *`r Sys.info()["user"]`*.

@@
